A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-08-18 01_TrialsForInclusionInAnalysis.Rmd
copy edits

   1. A field trial testing the efficacy of fungicide on powdery mildew afflicted mungbean plants.  
   2. Trial data needed to include:  
      i) fungicide active ingredients.  
      ii) A Demethylase inhibitor (DMI) fungicide.  
      iii) The date at which powdery mildew first appeared in the trial.  
      iv) Disease severity at the end of the growing seasons.  
      v) Fungicide application dates.  
      vi) fungicide dose.  
      vii) Crop yield.  
      viii) Treatment means and accompanying variance

@@

We will retain the follow trials which only contain DMI fungicides. 
However we won't remove non-DMI fungicides just yet, we will do this before the analysis. 
```{r}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref, location, year)%>%
   arrange(year)
```

@@

Finally we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis. 
```{r classifyData}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(trial_ref = as.character(trial_ref)) %>%
   mutate(year = as.character(year)) %>%
   mutate(location = as.character(location)) %>%
   mutate(host_genotype = as.character(host_genotype)) %>%
   mutate(row_spacing = as.double(round(row_spacing, digits = 2))) %>%
   mutate(replicates = as.integer(replicates)) %>%
   mutate(planting_date = ymd(planting_date)) %>%
   mutate(flowering_date = ymd(flowering_date)) %>%
   mutate(pod_fill_date = ymd(pod_fill_date)) %>%
   mutate(mid_late_pod_fill = ymd(mid_late_pod_fill)) %>%
   mutate(first_sign_disease = ymd(first_sign_disease)) %>%
   mutate(fungicide_ai = as.character(fungicide_ai))%>%
   mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2))%>%
   mutate(fungicide_application_1 = ymd(fungicide_application_1)) %>%
   mutate(fungicide_application_2 = ymd(fungicide_application_2)) %>%
   mutate(fungicide_application_3 = ymd(fungicide_application_3)) %>%
   mutate(fungicide_application_4 = ymd(fungicide_application_4)) %>%
   mutate(fungicide_application_5 = ymd(fungicide_application_5)) %>%
   mutate(fungicide_application_6 = ymd(fungicide_application_6)) %>%
   mutate(total_fungicide = as.integer(total_fungicide)) %>%
   mutate(harvest_date = ymd(harvest_date)) %>%
   mutate(final_assessment = ymd(final_assessment)) %>%
   mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4))%>%
   mutate(disease_error = round(as.double(disease_error), digits = 6))%>%
   mutate(D_error_type = as.character(D_error_type))%>%
   mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4))%>%
   mutate(yield_error = round(as.double(yield_error), digits = 6))%>%
   mutate(Y_error_type = as.character(Y_error_type))%>%
   mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6))%>%
   mutate(yield_gain = round(as.double(yield_gain), digits = 4))%>%
   mutate(prop_YG = round(as.double(prop_YG), digits = 4))%>%
   select(-c(trial_design, # remove the following columns
             plot_length.m.,
             plot_width.m.,
             plant_density,
             trade_name,
             n_treatment,
             emergence_date,
             rating_scale,
             raw_graded,
             raw_data_avail,
             comments,
             days_harvest.planting,
             AUDPS_m,
             AUDPC_sd,
             Inc_Ms))
```

>>>>

   1. A field trial testing the efficacy of fungicide on powdery mildew afflicted mungbean plants.  
   2. Trial data needed to include:  
      i) fungicide active ingredients.  
      ii) A demethylase inhibitor (DMI) fungicide.  
      iii) The date at which powdery mildew first appeared in the trial.  
      iv) Disease severity at the end of the growing seasons.  
      v) Fungicide application dates.  
      vi) fungicide dose.  
      vii) Crop yield.  
      viii) Treatment means and accompanying variance

@@

We will retain the following trials, which only contain DMI fungicides. 
However, we won't remove non-DMI fungicides just yet, we will do this before the analysis.

```{r}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref, location, year)%>%
   arrange(year)
```

@@

Finally we are going to define the class of each variable in the data, retaining only the variables relevant to the analysis.

```{r classifyData}
PM_MB_dat <- 
   PM_MB_dat %>%
   mutate(trial_ref = as.character(trial_ref)) %>%
   mutate(year = as.character(year)) %>%
   mutate(location = as.character(location)) %>%
   mutate(host_genotype = as.character(host_genotype)) %>%
   mutate(row_spacing = as.double(round(row_spacing, digits = 2))) %>%
   mutate(replicates = as.integer(replicates)) %>%
   mutate(planting_date = ymd(planting_date)) %>%
   mutate(flowering_date = ymd(flowering_date)) %>%
   mutate(pod_fill_date = ymd(pod_fill_date)) %>%
   mutate(mid_late_pod_fill = ymd(mid_late_pod_fill)) %>%
   mutate(first_sign_disease = ymd(first_sign_disease)) %>%
   mutate(fungicide_ai = as.character(fungicide_ai))%>%
   mutate(dose_ai.ha = round(as.double(dose_ai.ha), digits = 2))%>%
   mutate(fungicide_application_1 = ymd(fungicide_application_1)) %>%
   mutate(fungicide_application_2 = ymd(fungicide_application_2)) %>%
   mutate(fungicide_application_3 = ymd(fungicide_application_3)) %>%
   mutate(fungicide_application_4 = ymd(fungicide_application_4)) %>%
   mutate(fungicide_application_5 = ymd(fungicide_application_5)) %>%
   mutate(fungicide_application_6 = ymd(fungicide_application_6)) %>%
   mutate(total_fungicide = as.integer(total_fungicide)) %>%
   mutate(harvest_date = ymd(harvest_date)) %>%
   mutate(final_assessment = ymd(final_assessment)) %>%
   mutate(PM_final_severity = round(as.double(PM_final_severity), digits = 4))%>%
   mutate(disease_error = round(as.double(disease_error), digits = 6))%>%
   mutate(D_error_type = as.character(D_error_type))%>%
   mutate(grain_yield.t.ha. = round(as.double(grain_yield.t.ha.), digits = 4))%>%
   mutate(yield_error = round(as.double(yield_error), digits = 6))%>%
   mutate(Y_error_type = as.character(Y_error_type))%>%
   mutate(Y_Msquare = round(as.double(Y_Msquare), digits = 6))%>%
   mutate(yield_gain = round(as.double(yield_gain), digits = 4))%>%
   mutate(prop_YG = round(as.double(prop_YG), digits = 4))%>%
   select(-c(trial_design, # remove the following columns
             plot_length.m.,
             plot_width.m.,
             plant_density,
             trade_name,
             n_treatment,
             emergence_date,
             rating_scale,
             raw_graded,
             raw_data_avail,
             comments,
             days_harvest.planting,
             AUDPS_m,
             AUDPC_sd,
             Inc_Ms))
```
